---
title: "Recla analysis - determining the LRT statistics & p-values"
author: "Frederick Boehm"
date: "3/7/2018"
output: github_document
---

In this document, we use the 1000 files (for each of the bivariate traits) that each contain a likelihood ratio test statistic for a bootstrap sample. 


## Load the scan_pvl results for each of the 3 bivariate traits

```{r}
library(dplyr)
as_tibble(read.table("../results/2018-02-27_pvl-LD_distance_light-HP_latency-chr8-sex.txt")) -> out_0722
as_tibble(read.table("../results/2018-02-27_pvl-LD_distance_light-LD_light_pct-chr8-sex.txt")) -> out_0710
as_tibble(read.table("../results/2018-02-27_pvl-LD_light_pct-HP_latency-chr8-sex.txt")) -> out_1022
```

```{r}
library(qtl2pleio)
calc_lrt_tib(out_0722) # run 552
calc_lrt_tib(out_0710) # run 553
calc_lrt_tib(out_1022) # run 551
```


## Working with the CHTC results files

Our bootstrap samples were each analyzed with computing resources from the Center for High-Throughput Computing (CHTC) at UW-Madison.

```{bash}
ls ../chtc/Recla-bootstrap/results-chtc/boot-run551/*.txt | wc
ls ../chtc/Recla-bootstrap/results-chtc/boot-run552/*.txt | wc
ls ../chtc/Recla-bootstrap/results-chtc/boot-run553/*.txt | wc
```

We see that each directory has the required 1000 files. 


### Run 551

```{r}
directory <- "../chtc/Recla-bootstrap/results-chtc/boot-run551"
fns <- dir(directory)
i <- 1
out <- list()
for (fn in fns){
  full_fn <- file.path(directory, fn)
  read.table(full_fn) -> out[[i]]
  i <- i + 1
}
sum(do.call("rbind", out) > calc_lrt_tib(out_1022))
```


## Run 552

```{r}
directory <- "../chtc/Recla-bootstrap/results-chtc/boot-run552"
fns <- dir(directory)
i <- 1
out <- list()
for (fn in fns){
  full_fn <- file.path(directory, fn)
  read.table(full_fn) -> out[[i]]
  i <- i + 1
}
sum(do.call("rbind", out) > calc_lrt_tib(out_0722))
```


## Run 553

```{r}
directory <- "../chtc/Recla-bootstrap/results-chtc/boot-run553"
fns <- dir(directory)
i <- 1
out <- list()
for (fn in fns){
  full_fn <- file.path(directory, fn)
  read.table(full_fn) -> out[[i]]
  i <- i + 1
}
sum(do.call("rbind", out) > calc_lrt_tib(out_0710))
```

